---
title: "CNEA.CleanR"
author: "Charlotte S."
date: "7 février 2018"
output: 
  html_document:
    code_folding: hide
runtime: shiny
---


```{r include=FALSE, cache=FALSE}
# function to ask for the background values
is.null.vector <- function(x) {
  sapply(x, is.null)
}
separateAnalysis_CNEA <- function(data, column1, column2) {
  
  vect1 <- which(is.na(column1))
  listPlace1 <- successiveValues(vect1)
  
  vect2 <- which(is.na(column2))
  listPlace2 <- successiveValues(vect2)
  
  if(length(listPlace1) != 0 | length(listPlace2) != 0) {
    
    if(length(listPlace1) == length(listPlace2)) {

    toReturn <-  lapply(1:length(listPlace1), function(x) {
      data[c(listPlace1[[x]],listPlace2[[x]]), ]
    })

  } else {
    toReturn <- NULL
  }
  } else {
      toReturn <- NULL
    }
  
  
  return(toReturn)
}

successiveValues = function(vect) {
                          
                          if(length(vect) != 1) {
                            
                            length.vect <- length(vect)
                            
                            i <- 1
                            k <- 1
                            
                            finalList <- list()
                            
                            while(i < length.vect) {
                              
                              finalList[k][[1]] <- vect[i]
                              
                              while(vect[i + 1] == vect[i] +1 & i < length.vect) {
                                
                                finalList[k][[1]] <- c(finalList[k][[1]], vect[i+1])
                                
                                i <- i+1
                                
                              }
                              
                              i <- i+1
                              k <- k+1
                              
                            }
                            
                            if(length(unlist(finalList)) != length.vect) {
                              finalList[[k]] <- vect[length.vect]
                            }
                            
                          } else {
                            finalList <- list(vect)
                          }
                          

                          
                          return(finalList)
                          
}

                        # some helpful threads
                        # https://stat.ethz.ch/pipermail/r-help/2008-September/172641.html
                        # http://tolstoy.newcastle.edu.au/R/e4/help/08/02/4875.html
                        # http://tolstoy.newcastle.edu.au/R/e2/help/07/01/8598.html
                        
                        # http://www.r-statistics.com/wp-content/uploads/2011/01/boxplot-add-label-for-outliers.r.txt
                        
                        # last updated: 31.10.2011
                        # 		This is instead of the 20.6.11 version...
                        
boxplot.with.outlier.label <- function(y, label_name, ..., spread_text = T, data, plot = T, range = 1.5, label.col = "blue", push_text_right = 1.3, # enlarge push_text_right in order to push the text labels further from their point
                                                               segement_width_as_percent_of_label_dist = .45, # Change this if you want to have the line closer to the label (range should be between 0 to 1
                                                               jitter_if_duplicate = T, jitter_only_positive_duplicates = F)
                        {	
                          # notes - this functions doesn't work if there are any missing values in the data.
                          #		You must pre-process the data to make sure it is "complete".
                          
                          
                          # change log:
                          # 19.04.2011 - added support to "names" and "at" parameters.
                          
                          
                          # jitter_if_duplicate - will jitter (Actually just add a bit of numbers) so to be able to decide on which location to plot the label when having identical variables...
                          require(plyr) # for is.formula and ddply
                          
                          # a function to jitter data in case of ties in Y's
                          jitter.duplicate <- function(x, only_positive = F)
                          {
                            if(only_positive) {
                              ss <- x > 0
                            } else {
                              ss <- T
                            }	
                            ss_dup <- duplicated(x[ss])
                            # ss <- ss & ss_dup
                            temp_length <- length(x[ss][ss_dup])	
                            x[ss][ss_dup] <- x[ss][ss_dup] + seq(from = 0.00001, to = 0.00002, length.out = temp_length)
                            x
                          }
                          # jitter.duplicate(c(1:5))
                          # jitter.duplicate(c(1:5,5,2))
                          # duplicated(jitter.duplicate(c(1:5,5,2)))
                          # jitter.duplicate(c(0,0,1:5,5,2))
                          # duplicated(jitter.duplicate(c(0,0,1:5,5,2)))
                          
                          
                          
                          # handle cases where 
                          if(jitter_if_duplicate) {
                            # warning("duplicate jutter of values in y is ON")
                            if(!missing(data)) {	#e.g: we DO have data
                              # if(exists("y") && is.formula(y)) {		# F && NULL # F & NULL
                              y_name <- as.character(substitute(y))	# I could have also used as.list(match.call())
                              # credit to Uwe Ligges and Marc Schwartz for the help
                              # https://mail.google.com/mail/?shva=1#inbox/12dd7ca2f9bfbc39
                              if(length(y_name) > 1) {	# then it is a formula (for example: "~", "y", "x"
                                model_frame_y <- model.frame(y, data = data)
                                temp_y <- model_frame_y[,1]
                                temp_y  <- jitter.duplicate(temp_y, jitter_only_positive_duplicates)	# notice that the default of the function is to work only with positive values...
                                # the_txt <- paste(names(model_frame_y)[1], "temp_y", sep = "<<-") # wrong...
                                the_txt <- paste("data['",names(model_frame_y)[1],"'] <- temp_y", sep = "")				
                                eval(parse(text = the_txt))	# jutter out y var so to be able to handle identical values.
                              } else {	# this isn't a formula
                                data[,y_name] <- jitter.duplicate(data[,y_name], jitter_only_positive_duplicates)
                                y <- data[,y_name]	# this will make it possible for boxplot(y, data) to work later (since it is not supposed to work with data when it's not a formula, but now it does :))
                              }		
                            } else {	# there is no "data"		 
                              if(is.formula(y)) { # if(exists("y") && is.formula(y)) {		# F && NULL # F & NULL
                                temp_y <- model.frame(y)[,1]
                                temp_y  <- jitter.duplicate(temp_y, jitter_only_positive_duplicates)	# notice that the default of the function is to work only with positive values...
                                temp_y_name <- names(model.frame(y))[1]	# we must extract the "names" before introducing a new enbironment (or there will be an error)
                                environment(y) <- new.env()
                                assign(temp_y_name, temp_y, environment(y))
                                # Credit and thanks for doing this goes to Niels Richard Hansen (2 Jan 30, 2011)
                                # http://r.789695.n4.nabble.com/environment-question-changing-variables-from-a-formula-through-model-frame-td3246608.html
                                # warning("Your original variable (in the global environemnt) was just jittered.")	# maybe I should add a user input before doing this....
                                # the_txt <- paste(names(model_frame_y)[1], "temp_y", sep = "<<-")
                                # eval(parse(text = the_txt))	# jutter out y var so to be able to handle identical values.
                              } else {
                                y <- jitter.duplicate(y, jitter_only_positive_duplicates)
                              }		
                            }
                          }
                          # the_txt <- paste("print(",names(model_frame_y)[1], ")")
                          # eval(parse(text = the_txt))	# jutter out y var so to be able to handle identical values.
                          # print(ls())
                          
                          
                          # y should be a formula of the type: y~x, y~a*b
                          # or it could be simply y
                          if(missing(data)) {
                            boxdata <- boxplot(y, plot = plot,range = range ,...)
                          } else {
                            boxdata <- boxplot(y, plot = plot,data = data, range = range ,...)
                          }
                          if(length(boxdata$names) == 1 && boxdata$names =="") boxdata$names <- 1	# this is for cases of type: boxplot(y) (when there is no dependent group)
                          if(length(boxdata$out) == 0 ) {
                            warning("No outliers detected for this boxplot")
                            return(invisible())
                          }
                          
                          if(!missing(data)) attach(data)	# this might lead to problams I should check out for alternatives for using attach here...
                          
                          
                          # creating a data.frame with information from the boxplot output about the outliers (location and group)
                          boxdata_group_name <- factor(boxdata$group)
                          levels(boxdata_group_name) <- boxdata$names[as.numeric(levels(boxdata_group_name))]	# the subseting is for cases where we have some sub groups with no outliers
                          if(!is.null(list(...)$at))	{	# if the user chose to use the "at" parameter, then we would like the function to still function (added on 19.04.2011)
                            boxdata$group <- list(...)$at[boxdata$group]		
                          }
                          boxdata_outlier_df <- data.frame(group = boxdata_group_name, y = boxdata$out, x = boxdata$group)
                          
                          
                          # Let's extract the x,y variables from the formula:
                          if(is.formula(y))
                          {
                            model_frame_y <- model.frame(y)
                            # old solution: (which caused problems if we used the names parameter when using a 2 way formula... (since the order of the names is different then the levels order we get from using factor)
                            # y <- model_frame_y[,1]
                            # x <- model_frame_y[,-1]
                            
                            y <- model_frame_y[,1]
                            x <- model_frame_y[,-1]
                            if(!is.null(dim(x))) {	# then x is a matrix/data.frame of the type x1*x2*..and so on - and we should merge all the variations...
                              x <- apply(x,1, paste, collapse = ".")
                            }
                          } else {
                            # if(missing(x)) x <- rep(1, length(y))
                            x <- rep(1, length(y))	# we do this in case y comes as a vector and without x
                          }	
                          
                          # and put all the variables (x, y, and outlier label name) into one data.frame
                          DATA <- data.frame(label_name, x ,y)
                          
                          if(!is.null(list(...)$names))	{	# if the user chose to use the names parameter, then we would like the function to still function (added on 19.04.2011)
                            DATA$x <- factor(DATA$x, levels = unique(DATA$x))
                            levels(DATA$x) = list(...)$names	# enable us to handle when the user adds the "names" parameter # fixed on 19.04.11	# notice that DATA$x must be of the "correct" order (that's why I used split above
                            # warning("Careful, the use of the 'names' parameter is experimental.  If you notice any errors please e-mail me at: tal.galili@gmail.com")
                          }
                          
                          if(!missing(data)) detach(data)	# we don't need to have "data" attached anymore.
                          
                          # let's only keep the rows with our outliers 
                          boxplot.outlier.data <- function(xx, y_name = "y")
                          {
                            y <- xx[,y_name]
                            boxplot_range <- range(boxplot.stats(y, coef = range )$stats)
                            ss <- (y < boxplot_range[1]) | (y > boxplot_range[2])
                            return(xx[ss,])	
                          }
                          outlier_df <-ddply(DATA, .(x), boxplot.outlier.data)
                          
                          
                          # create propor x/y locations to handle over-laping dots...
                          if(spread_text) {
                            # credit: Greg Snow
                            require(TeachingDemos)		
                            temp_x <- boxdata_outlier_df[,"x"]
                            temp_y1 <- boxdata_outlier_df[,"y"]
                            temp_y2 <- temp_y1
                            for(i in unique(temp_x))
                            {
                              tmp <- temp_x == i
                              temp_y2[ tmp ] <- spread.labs( temp_y2[ tmp ], 1.3*strheight('A'), maxiter=6000, stepsize = 0.05) #, min=0 )
                            }
                            
                          }
                          
                          
                          
                          # max(strwidth(c("asa", "a"))
                          # move_text_right <- max(strwidth(outlier_df[,"label_name"]))	
                          
                          # plotting the outlier labels :)  (I wish there was a non-loop wise way for doing this)
                          for(i in seq_len(dim(boxdata_outlier_df)[1]))
                          {
                            # ss <- (outlier_df[,"x"]  %in% boxdata_outlier_df[i,]$group) & (outlier_df[,"y"] %in% boxdata_outlier_df[i,]$y)
                            
                            # if(jitter_if_duplicate) {
                            # ss <- (outlier_df[,"x"]  %in% boxdata_outlier_df[i,]$group) & closest.number(outlier_df[,"y"]  boxdata_outlier_df[i,]$y)
                            # } else {
                            ss <- (outlier_df[,"x"]  %in% boxdata_outlier_df[i,]$group) & (outlier_df[,"y"] %in% boxdata_outlier_df[i,]$y)
                            # }
                            
                            current_label <- outlier_df[ss,"label_name"]
                            temp_x <- boxdata_outlier_df[i,"x"]
                            temp_y <- boxdata_outlier_df[i,"y"]		
                            # cbind(boxdata_outlier_df,		temp_y2)
                            # outlier_df
                            
                            
                            
                            if(spread_text) {
                              temp_y_new <- temp_y2[i] # not ss			
                              move_text_right <- strwidth(current_label) * push_text_right
                              text( temp_x+move_text_right, temp_y_new, current_label, col = label.col)			
                              # strwidth
                              segments( temp_x+(move_text_right/6), temp_y, temp_x+(move_text_right*segement_width_as_percent_of_label_dist), temp_y_new )
                            } else {
                              text(temp_x, temp_y, current_label, pos = 4, col = label.col)
                            }		
                          }
                          
                          # outputing some of the information we collected
                          invisible(list(boxdata = boxdata, boxdata_outlier_df = boxdata_outlier_df, outlier_df=outlier_df))
                        }

complementVector = function(VectR, x) {
                          
                          length.VectR <- length(VectR)
                          length.x <- length(x)
                          
                          y <- vector() #output
                          
                          for(i in 1:length.VectR) {
                            
                            if(is.na(match(VectR[i], x))) {
                              y <- c(y, i)
                            } else {}
                            
                          }
                          
                          return(VectR[y])
                          
                        }
blank.correction <- function(Area.blank, Sign.blank, Area.sample, Sign.sample) {
  value <- (Area.sample*Sign.sample - Area.blank*Sign.blank)/(Area.sample - Area.blank)
  return(value)
}
Area.correction <- function(value.toCorrect, dilution) {
  value <- value.toCorrect * (1+dilution/100)
  return(value)
}
Karina.Normalisation <- function(signature, true.Values, real.Values){
  coef <- (true.Values[1] - true.Values[2])/(real.Values[1]-real.Values[2])
  
  value <- (signature - real.Values[2]) * coef + true.Values[2]
  
  return(value)
}
Peter.Correction.d15N <- function(signature, rank, slope, intercept) {
  newValue <- signature - (slope * rank + intercept - 5.4) 
  return(newValue)
}
Peter.Correction.d13C <- function(signature, rank, slope, intercept) {
  newValue <- signature - (slope * rank + intercept + 21.8) 
  return(newValue)
}
max.list = function(liste) {
                          
                          max.list <- 0
                          
                          n <- length(liste)
                          
                          for (i in 1:n) {
                            
                            max.Prov <- length(liste[[i]])
                            
                            if(max.Prov > max.list) {max.list <- max.Prov} else {}
                            
                          }
                          
                          return(max.list)
                        }
```
<br><br>

### To read beforhand

**Aim of this document:** This sheet has been created to help users to format the CN_EA file in order to upload it for further calculations. <br><br>
**WARNING:** The aim of CN_EA.CleanR is **not** to correct automatically the CN_EA file, this delicated task requiring human skills. However, it is dedicated to point out errors or abnormalities of the raw CN_EA file. When the first round of correction has been finished and before uploading any file in isoSignature.creatR, please check a last time with CN_EA.CleanR that there is **NO** error in the required **CONCLUSIONS** (this task may require several rounds of CN_EA.CleanR).
**WARNING:** The weight file and the CNEA have to list the sample in the same order.
<br><br>

------------------------------------------------------------------------------------------------------------------------------

### Cleaning and calculation settings 
<br>
```{r echo = F} 

output$info <- renderUI({
  div(column(6,
             fileInput("CNEA", label = p("Select the CNEA file")),
             textInput("nameSession", label = "", value = "Name of the session"),
             textInput("dateProcessig", label = "", value = "Date of the analysis:"),
             textInput("Responsible", label = "", value = "Responsible:"),
             textInput("Temperature", label = "", value = "Lab Temperature:"),
             textInput("SampleName", label = "", value = "Sample name:"),
             textInput("system", label = "", value = "System:"),
             textInput("Column", label = "", value = "Column:"),
             textInput("temp.Owen", label = "", value = "Temp Owen:")
             ), 
      (column(6,
              fileInput("weightData", label = p("Select the weight file")),
              textInput("carrier.Gas", label = "", value = "Carrier gas:"),
              textInput("carrier.flow", label = "", value = "Carrier flow:"),
              textInput("Reference.gas1", label = "", value = "Reference gas 1:"),
              textInput("Reference.flow1", label = "", value = "Reference flow1:"),
              textInput("Reference.gas2", label = "", value = "Reference gas 2:"),
              textInput("Reference.flow2", label = "", value = "Reference flow2:"),
              textInput("Method", label = "", value = "Method:")
      )
      )
  )
})

output$selectSample <- renderUI({
  
  if(!is.null(input$CNEA)) {
  
  level.identifier.1 <- levels(CNEA()$Identifier.1)
  
  div(column(12,
             br(),
             checkboxGroupInput("sample", label = p("Select the name(s) that correspond to samples"),
                                choices = level.identifier.1,
                                selected = level.identifier.1[1], 
                                inline = T )
  ))
  
} else {}
  
})
```
`r uiOutput("info")` 
<br><br>
`r uiOutput("selectSample")`
<br><br>

```{r}
CNEA <- reactive({
  if(!is.null(input$CNEA)) {
    CNEA <- read.xls (input$CNEA$datapath, sheet = 1, header = TRUE)

    Rank.Analysis <- 2: (nrow(CNEA)+ 1) # +1 to make the excel file correspond to the R file

    CNEA <- cbind(Rank.Analysis, CNEA)

    bad.Id1 <- which(CNEA$Identifier.1 == "" | is.na(CNEA$Identifier.1) | is.null(CNEA$Identifier.1))

    if(length(bad.Id1) != 0) {
      CNEA <- CNEA[-bad.Id1, ]
    } else {}

    return(CNEA)

  }
})

weightData <- reactive({
  if(!is.null(input$weightData)) {
    weightData <- read.xls (input$weightData$datapath, sheet = 1, header = TRUE)

    weightData$Box.pos <- as.character(weightData$Box.pos)

    return(weightData)
  }
})

############################
## Condition 1: identifier.1
############################

bad.Id1 <- reactive({

  if(!is.null(input$CNEA)) {

    CNEA <- read.xls (input$CNEA$datapath, sheet = 1, header = TRUE)

    level.identifier.1 <- levels(CNEA$Identifier.1)

    bad.Id1 <- which(CNEA$Identifier.1 == "" | is.na(CNEA$Identifier.1) | is.null(CNEA$Identifier.1))

    return(bad.Id1)

  } else {}
})

output$id1_Error <- renderText({

  if(!is.null(input$CNEA)) {

    if(length(bad.Id1()) != 0) {

      toDisplay.1 <- paste("Some identifier.1 are empty. Please remove the line:", paste(bad.Id1(), sep = " ", collapse = ""))

    } else {NULL}

  } else {}

})

output$id1_OK <- renderText({

  if(!is.null(input$CNEA)) {

  if(length(bad.Id1()) != 0) {NULL} else {
    toDisplay.1 <- "No problem in the identifier.1"
  }
  } else {}
})

############################
## Condition 7: identifier.1
############################

error.area <- reactive({

  if(!is.null(input$CNEA)) {

    error.area <- which(is.null.vector(CNEA()$Area.All) | is.na(CNEA()$Area.All) | CNEA()$Area.All == "NA" | CNEA()$Area.All == "")

    return(error.area)

  } else {}
})

output$error.area_Error <- renderText({

  if(!is.null(input$CNEA)) {

    if(length(error.area()) != 0) {

      toDisplay.1 <- paste("Some Area are empty. Please remove the line:", paste(error.area(), sep = " ", collapse = ""))

    } else {NULL}

  } else {}

})

output$error.area_OK <- renderText({

  if(!is.null(input$CNEA)) {

  if(length(error.area()) != 0) {
    NULL
    } else {
      toDisplay.1 <- "No problem in the Area"
    }
    
  } else {}
})

############################
## Condition 2
############################

resultMatrix <- reactive({

  if(!is.null(input$CNEA)){

    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)

    CNEA.liste <- CNEA.liste[which(names(CNEA.liste) != "")]

    sample <- input$sample

    resultMatrix <- matrix(NA,ncol = 13) #the matrix summurizing the number of values in the rArea

    NbValue.C <- NULL #number of signature for C
    NbValue.N <- NULL #number of signature for N

    Nb.dilution <- NULL #nb of dilution
    Nb.dilution.Diff0 <- NULL #nb dilution different of 0
    
    error.id2 <- NULL # test that all the Identifier.2 are identicals
    error.id2.sample <- NULL # test that all the sample have a not empty

    for(i in 1:length(CNEA.liste)) {

      dataProv <- CNEA.liste[[i]]

      Sep.Analysis <- separateAnalysis_CNEA(dataProv, column1 = dataProv$d.13C.12C, column2 = dataProv$d.15N.14N)

      number.Analysis <- length(Sep.Analysis)

      for(j in 1:number.Analysis) {
        
        One.Analysis <- as.data.frame(Sep.Analysis[[j]])
        
        if(length(unique(One.Analysis$Identifier.2)) == 1) {
          error.id2 <- 0
          } else {
            error.id2 <- 1
            } ### 0 = all the Identifier.2 are identicals, 1 = at least one line has a different Identifier.2
        
        cond <- sapply(1:length(sample), function(x) {length(which(names(CNEA.liste)[i] == sample[x]))})
        
        cond1 <- length(which(cond != 0)) # marker that it's a sample
        
        cond2 <-   length(which(is.null.vector(One.Analysis$Identifier.2) | is.na(One.Analysis$Identifier.2) | One.Analysis$Identifier.2 == "NA" | One.Analysis$Identifier.2 == ""))
        
        if(cond1 != 0 & cond2 != 0) {
          error.id2.sample <- 1
          } else {
            error.id2.sample <- 0
            } ### 0 = no sample id2 is empty, 1 = at least one line of the sample id2 is empty
        

        ### deal with dilution

        dilution <- One.Analysis$Sample.Dilution

        dilution.Diff0 <- dilution[which(dilution != 0)]

        Nb.dilution <- length(unique(dilution.Diff0))

        NbValue.C <- which(!is.na(One.Analysis$d.13C.12C) & !is.null(One.Analysis$d.13C.12C) & One.Analysis$d.13C.12C != "")
        NbValue.N <- which(!is.na(One.Analysis$d.15N.14N) & !is.null(One.Analysis$d.15N.14N) & One.Analysis$d.15N.14N != "")

        toAdd <- c(names(CNEA.liste)[i], as.character(One.Analysis$Identifier.2[1]), as.numeric(as.character(One.Analysis$Rank.Analysis[1])), error.id2, error.id2.sample,length(NbValue.C), length(NbValue.N), Nb.dilution, dilution.Diff0[1], One.Analysis$Area.All[NbValue.N[length(NbValue.N)]], One.Analysis$Area.All[NbValue.C[1]], One.Analysis$d.15N.14N[NbValue.N[length(NbValue.N)]], One.Analysis$d.13C.12C[NbValue.C[1]])
        
        resultMatrix <- rbind(resultMatrix, toAdd)
      }
    }

    resultMatrix <- resultMatrix[-1,]
    colnames(resultMatrix) <- c("Identifier.1", "Identifier.2","FirstLine", "error.id2", "error.id2.sample","NbValue.C", "NbValue.N", "Nb.dilution", "Dilution", "Area.N", "Area.C","d15N", "d13C")
    rownames(resultMatrix) <- 1:nrow(resultMatrix)
    resultMatrix <- as.data.frame(resultMatrix)

    for(i in 3:ncol(resultMatrix)){
      resultMatrix[,i] <- as.numeric(as.character(resultMatrix[,i]))
    }

      resultMatrix <- resultMatrix[order(resultMatrix[,3]),]
      
      return(resultMatrix)

  } else {}

})

output$nbValue.C_Error <- renderText({
  if(!is.null(input$CNEA)){
    
    errorC <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.C == 0)]
    
    if(length(errorC) != 0) {
       paste("There is no value for C in the analysis. Please check the line(s)", paste(errorC, sep = " ", collapse = " "))
    } else { NULL }
    
  } else {}
})

output$nbValue.C_OK <- renderText({
  if(!is.null(input$CNEA)){
    
    errorC <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.C == 0)]
    
    if(length(errorC) == 0) {
       "There is at least one C signature for every analysis"
    } else { NULL }
    
  } else {}
})

output$nbValue.N_Error <- renderText({
  if(!is.null(input$CNEA)){
    
    errorN <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N == 0)]
    
    if(length(errorN) != 0) {
       paste("There is no value for N in the analysis. Please check the line(s)", paste(errorN, sep = " ", collapse = " "))
    } else { NULL }
    
  } else {}
})

output$nbValue.N_OK <- renderText({
  if(!is.null(input$CNEA)){
    
    errorN <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N == 0)]
    
    if(length(errorN) == 0) {
       "There is at least one N signature for every analysis"
    } else { NULL }
    
  } else {}
})

############################
## Condition 3: Identifier.2
############################

dataTables <- reactive({

  if(!is.null(input$CNEA)) {

    sample <- input$sample

    place <- NULL

    for(x in 1:length(sample)) {

      if(x == 1) {
        CNEA.sample <- resultMatrix()[which(resultMatrix()$Identifier.1 == sample[x]), ]
        place <- which(resultMatrix()$Identifier.1 == sample[x])
      } else {
         CNEA.sample <- rbind(CNEA.sample, resultMatrix()[which(resultMatrix()$Identifier.1 == sample[x]), ])
        place <- c(place, which(resultMatrix()$Identifier.1 == sample[x]))
      }
    }

    place <- sort(place)

    PlaceBar <- complementVector(1:nrow(resultMatrix()), place)

    CNEA.sample <- CNEA.sample[order(CNEA.sample$FirstLine),] # data with only the sample

    CNEA.standard <- resultMatrix()[PlaceBar, ] # data with only the standards

    return(list(CNEA.sample, CNEA.standard))

  } else {}
})

dataStandard <- reactive({

  if(!is.null(input$CNEA)) {

   dataTables()[[2]]

  } else {}
})

dataSample <- reactive({

  if(!is.null(input$CNEA)) {

   dataTables()[[1]]

  } else {}
})

output$dataSampleToPrint <- renderDT({

  if(!is.null(input$CNEA)) {

    dataSample()[, c(1,2,3,9,10,11, 12,13)]

  } else {}
})

output$dataStandardToPrint <- renderDT({

  if(!is.null(input$CNEA)) {

    dataStandard()[, c(1,3,9,10,11, 12, 13)]

  } else {}
})

output$error_id.2_Error <- renderText({

  if(!is.null(input$CNEA)) {

    error_id.2 <- resultMatrix()$FirstLine[which(resultMatrix()$error_id.2 != 0)]

    if(length(error_id.2) != 0) {
    paste("Some analysis show different name in their identifier.2. Please check in the analysis line(s)", paste(error_id.2, sep = " ", collapse = " "))
    } else {}

  } else {}
})

output$error_id.2_OK <- renderText({

  if(!is.null(input$CNEA)) {

  error_id.2 <- resultMatrix()$FirstLine[which(resultMatrix()$error_id.2 != 0)]

  if(length(error_id.2) == 0) {
    "All the identifier.2 values are identical within a single analysis"
  } else {}

  } else {}
})

output$error.id2.sample_Error <- renderText({

  if(!is.null(input$CNEA)) {

  error.id2.sample <- resultMatrix()$FirstLine[which(resultMatrix()$error.id2.sample != 0)]

  if(length(error.id2.sample) != 0) {
    paste("Some analysis show an empty identifier.2. Please check in the analysis line(s)", paste(error.id2.sample, sep = " ", collapse = " "))
  } else {}

  } else {}

})

output$error.id2.sample_OK <- renderText({

  if(!is.null(input$CNEA)) {

  error.id2.sample <- resultMatrix()$FirstLine[which(resultMatrix()$error.id2.sample != 0)]

  if(length(error.id2.sample) == 0) {
        "No identifier is empty in sample, great :)"
  } else {}

  } else {}

})

############################
## Condition 4: dilution
############################

output$dilution_Error <- renderText({
  
  if(!is.null(input$CNEA)){
    
    err <- resultMatrix()$FirstLine[which(resultMatrix()$Nb.dilution != 1)]
    
    if(length(err) != 0) {
      paste("There is a mistake in the dilution factor. Please check line(s)", paste(err, sep = "", collapse = " "))
    } else {NULL}
    
  } else {}
  
})

output$dilution_OK <- renderText({
  
  if(!is.null(input$CNEA)){
    
    err <- resultMatrix()$FirstLine[which(resultMatrix()$Nb.dilution != 1)]
    
    if(length(err) == 0) {
      "Everything is ok regarding dilution"
    } else {NULL}
    
  } else {}
  
})

############################
## Condition 5: secondary condition 
############################

output$Value.N.sec_Error <- renderText({
  
  if(!is.null(input$CNEA)){
    
    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)

    CNEA.liste <- CNEA.liste[which(names(CNEA.liste) != "")]
    
    sucrose <- names(CNEA.liste)[str_detect(names(CNEA.liste), "ucrose")]
    
    errSucr <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N != 3 & resultMatrix()$Identifier.1 == sucrose)]
    err <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N != 4 & resultMatrix()$Identifier.1 != sucrose)]
    
    E <- c(errSucr, err)
    
    if(length(E) != 0) {
      paste("Some analysis showed unusual number of N signatures. Please check line(s)", paste(E, sep = "", collapse = " "))
    } else {NULL}
    
  } else {}
  
})

output$Value.N.sec_OK <- renderText({
  
  if(!is.null(input$CNEA)){
    
    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)

    CNEA.liste <- CNEA.liste[which(names(CNEA.liste) != "")]
    
    sucrose <- names(CNEA.liste)[str_detect(names(CNEA.liste), "ucrose")]
    
    errSucr <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N != 3 & resultMatrix()$Identifier.1 == sucrose)]
    err <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N != 4 & resultMatrix()$Identifier.1 != sucrose)]
    
    E <- c(errSucr, err)
    
    if(length(E) == 0) {
      "The number of N signatures per analysis seems coherent"
    } else {NULL}
    
  } else {}
  
})

output$Value.C.sec_Error <- renderText({
  
  if(!is.null(input$CNEA)){
    
    err <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.C != 2)]
    
    if(length(err) != 0) {
      paste("Some analysis showed unusual number of C signatures. Please check line(s)", paste(err, sep = "", collapse = " "))
    } else {NULL}
    
  } else {}
  
})

output$Value.C.sec_OK <- renderText({
  
  if(!is.null(input$CNEA)){
    
    err <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.C != 2)]
    
    if(length(err) == 0) {
      "The number of C signatures per analysis seems coherent"
    } else {NULL}
    
  } else {}
  
})

############################
## Condition 6: secondary condition 
############################

Data_plus_weight <- reactive({ ## for pasting the weight of the sample

  if(!is.null(input$CNEA) & !is.null(input$weightData) & !is.null(resultMatrix())) {

  errorToCount <- 0 # flag for error
  line.flag <- NA

  Data_plus_weight <- NULL

  nRow.dataSample <- nrow(dataSample())

  nRow.weightData <- nrow(weightData())

  if(nRow.dataSample != nRow.weightData) {
    errorToCount <- 1
  } else {
      for(i in 1:nRow.dataSample){
        if(as.character(dataSample()$Identifier.2[i]) != as.character(weightData()$Box.pos[i])){
          errorToCount <- 1
          line.flag <- dataSample()$Identifier.2[i]
          } else {}
      }
      if(errorToCount == 0) {
        Data_plus_weight <- cbind(dataSample(), weightData()$Name, weightData()$Measured.Weigth..mg.)
        colnames(Data_plus_weight) <- c(colnames(dataSample()), "sampleName", "SampleWeight")
      } else {}
  }

  return(list(c(errorToCount, line.flag), Data_plus_weight))

  } else {}
})

output$weight_Error <- renderText({

  if(!is.null(input$CNEA) & !is.null(input$weightData)) {

  if(Data_plus_weight()[[1]][1] != 0){
    if(!is.na(Data_plus_weight()[[1]][2])){
      paste("Weight and CNEA files do not match on their identifier.2, check line(s):", paste(Data_plus_weight()[[1]][2], sep = " ", collapse = " "))
    } else {
            paste("Weight and CNEA files do not have the same number of rows")
    }
  } else {
    NULL
  }

  } else {}
})

output$weight_OK <- renderText({

  if(!is.null(input$CNEA) & !is.null(input$weightData)) {

  if(Data_plus_weight()[[1]][1] != 0){
      NULL
  } else {
    "The CNEA and weight file seem to match (Note that it did not check for the box name)"
  }

  } else {}
})

```


------------------------------------------------------------------------------------------------------------------------------

### Conditions tested for cleaning

Necessary conditions (i.e. corrections **mandatory** for IsoSignature.creatR)

1. Condition 1: Any identifier 1 should not be empty or null
`r textOutput("id1_OK")`
**`r textOutput("id1_Error")`**
<br>
2. Condition 2: One analysis (i.e. the ranks are following) must contain not empty Area.All cell. d13C/d12C and d15N/d14N should have each at least one value.
`r textOutput("nbValue.C_OK")`
**`r textOutput("nbValue.C_Error")`**
`r textOutput("nbValue.N_OK")`
**`r textOutput("nbValue.N_Error")`**
<br>
3. Condition 3: All identifier.2 of a single analysis should be not empty and identical (samples only)
**`r textOutput("error_id.2_Error")`**
`r textOutput("error_id.2_OK")`
**`r textOutput("error.id2.sample_Error")`**
`r textOutput("error.id2.sample_OK")`
<br>
4. Condition 4. Identifier.2 for weight and CNEA file should be in the same order (for sample only)
**`r textOutput("weight_Error")`**
`r textOutput("weight_OK")` 
<br>
4. Condition 5. No Area.All should be empty
**`r textOutput("error.area_Error")`**
`r textOutput("error.area_OK")`
<br>

Secondary conditions (i.e. corrections are not mandatory, CNEA.CleanR just mentionned them to warn user)

1. Analysis should have exactly one dilution value
`r textOutput("dilution_OK")`
**`r textOutput("dilution_Error")`**
<br>
2. Analysis should contain 4 signatures values (3 for the sucrose) for N and 2 for the carbone
`r textOutput("Value.N.sec_OK")`
**`r textOutput("Value.N.sec_Error")`**
`r textOutput("Value.C.sec_OK")`
**`r textOutput("Value.C.sec_Error")`**
<br><br>  

#### **Data Samples:**
<br>
`r DTOutput("dataSampleToPrint")`
<br><br>

#### **Data Standards:**
<br>
`r DTOutput("dataStandardToPrint")`
<br>

------------------------------------------------------------------------------------------------------------------------------

### Graphical detection of mistakes - Outlier highlighting
```{r}
output$forBoxPlot <- renderUI({
  if(!is.null(input$CNEA)) {

 level.identifier.1 <- levels(CNEA()$Identifier.1)

 checkboxGroupInput("toDisplay", label = "",
    choices = level.identifier.1,
    selected = level.identifier.1, 
     inline = T )

  } else {}

})

output$boxplot <- renderPlot({

  if(!is.null(input$CNEA)) {
    

    toDisplay <- input$toDisplay

    for(x in 1:length(toDisplay)) {

      if(x == 1) {
        dataTemp <- resultMatrix()[which(resultMatrix()$Identifier.1 == toDisplay[x]), ]
      } else {
         dataTemp <- rbind(dataTemp, resultMatrix()[which(resultMatrix()$Identifier.1 == toDisplay[x]), ])
      }
    }

    par(mfrow = c(1,2), mar = c(2,3,1.2,1.2))

    ylim.C  <- c(min(dataTemp$d13C, na.rm = T) - abs(min(dataTemp$d13C, na.rm = T))*0.1, max(dataTemp$d13C, na.rm = T) + abs(max(dataTemp$d13C, na.rm = T))*0.1)

    boxplot.with.outlier.label(as.numeric(as.character(dataTemp$d13C)), label_name = dataTemp$Identifier.2, ylim = ylim.C, cex = 1.25)

    mtext("d13C", side = 1)

    ylim.N  <- c(min(dataTemp$d15N, na.rm = T) - abs(min(dataTemp$d15N, na.rm = T))*0.1, max(dataTemp$d15N, na.rm = T) + abs(max(dataTemp$d15N, na.rm = T))*0.1)


    boxplot.with.outlier.label(as.numeric(as.character(dataTemp$d15N)), label_name = dataTemp$Identifier.2, ylim = ylim.N, cex = 1.25)

    mtext("d15N", side = 1)
    
    return(dataTemp)
  } else {}

})
```
`r uiOutput('forBoxPlot')`
`r plotOutput('boxplot')`
<br><br>

------------------------------------------------------------------------------------------------------------------------------

### Conclusions of the cleaning

```{r}
finalConclusion <- reactive({

  if(!is.null(resultMatrix())) {

  errorC <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.C == 0)]
  errorN <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N == 0)]

  error_id.2 <- resultMatrix()$FirstLine[which(resultMatrix()$error_id.2 != 0)]
  error.id2.sample <- resultMatrix()$FirstLine[which(resultMatrix()$error.id2.sample != 0)]

  errDilution <- resultMatrix()$FirstLine[which(resultMatrix()$Nb.dilution != 1)]

  CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)

  CNEA.liste <- CNEA.liste[which(names(CNEA.liste) != "")]
  sucrose <- names(CNEA.liste)[str_detect(names(CNEA.liste), "ucrose")]

  errSucr <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N != 3 & resultMatrix()$Identifier.1 == sucrose)]
  errSucr2 <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.N != 4 & resultMatrix()$Identifier.1 != sucrose)]

  E <- c(errSucr, errSucr2)

  errNbValueC <- resultMatrix()$FirstLine[which(resultMatrix()$NbValue.C != 2)]
  
  if(!is.null(Data_plus_weight())) {
    
      if(length(bad.Id1()) != 0 | length(error.area()) != 0 | length(errorC) != 0 | length(errorN) != 0 | length(error_id.2) != 0 | length(error.id2.sample) != 0 | length(errDilution) != 0 | length(E) != 0 | length(errNbValueC) != 0 | Data_plus_weight()[[1]][1] != 0) {
    return(TRUE)
  } else {return(FALSE)}
    
  } else {return(TRUE)}

  } else {return(TRUE)}


})

output$finalConclusion_error <- renderText({
  if(!is.null(resultMatrix())) {

  if(finalConclusion() == TRUE) {
    "There is at least one mistake in your files. <br> Please correct according to previously before continuing to read this file."
  } else {NULL}

  } else {NULL}
})

output$finalConclusion_OK <- renderText({

  if(!is.null(resultMatrix())) {
    
    if(finalConclusion() == FALSE) {
    "It seems that your files are correct."
    } else {NULL}
  } else {NULL}
  
})


```
`r textOutput("finalConclusion_OK")`
**`r span(htmlOutput("finalConclusion_error"), style="color:red")`**
<br>

------------------------------------------------------------------------------------------------------------------------------


### Settings for "IsotopeSignature.file" creation
**WARNING:** Before continuing in this file, please check the conditions above do **NOT** contain any error in required **CONCLUSIONS** (this task may require several run of utilisation of the function CNEA_cleanR). If the TCD file is upload without this last verification, CNEA_cleanR **CANNOT** garantee the validity of the following data.
<br><br>
`r uiOutput("info.2")`

```{r}
output$info.2 <- renderUI({
  
  if(!is.null(input$CNEA)) {
  
  CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
  
  blank <- names(CNEA.liste)[str_detect(names(CNEA.liste), "lank")]
  
  gelA <- weightData()$Name[(str_detect(weightData()$Name, "el") | str_detect(weightData()$Name, "EL"))]
  
  if(length(gelA) == 0) {
    gelA <- weightData()$Name[1]
  }
  
  backgroundValues <- c(0, 1167)
  
  div(
    checkboxGroupInput("blank", label = p("1. Select blanks (blank AND system blank)"), 
    choices = names(CNEA.liste),
    selected = blank,
    inline = T), 
    br(),
    checkboxGroupInput("gelA", label = p("2. Select Gel A"), 
    choices = levels(weightData()$Name),
    selected = gelA,
    inline =T),
     br(),
   tags$b("3. Background Values"),
    div(
        column(6, 
         textInput("Area.N.background", label = "", value = "Area of the blank N")),
        column(6,
         textInput("signature.N.background", label = "", value = "signature of the blank N"))),
    
    div(
      column(6, 
         textInput("Area.C.background", label = "", value = "Area of the blank C")),
      column(6,
         textInput("signature.C.background", label = "", value = "signature of the blank C")))
    )
  
  } else {}
  
})

nameInput.C <- reactive({
  
  if(!is.null(input$C.define)) {

  nameInput <- vector()

    for(i in 1:length(input$C.define)) {
      nameInput[i] <- paste0(resultMatrix()$Identifier.1[which(input$C.define[i] == resultMatrix()$Identifier.1)], "_inputName.C")
    }
  
  return(nameInput)
  
    
  }
  
})

output$chooseValue.C.stand <- renderUI({
  
  if(!is.null(input$CNEA) & !is.null(input$C.define)) {

  lapply(1:length(input$C.define), function(x){

    div(
      column(6, p(paste("Select the values that you want to keep for", resultMatrix()$Identifier.1[which(input$C.define[x] == resultMatrix()$Identifier.1)]))),
      column(6,
             checkboxGroupInput(nameInput.C()[x], label = p(""),
                                choices = resultMatrix()$d13C[which(input$C.define[x] == resultMatrix()$Identifier.1)],
                                selected = resultMatrix()$d13C[which(input$C.define[x] == resultMatrix()$Identifier.1)],
                                inline = T),
             br()
    )

    )
    })
  }
})

output$checkBox.C <- renderUI({
  
  if(!is.null(input$CNEA)) {
  
  CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
  
  level.identifier.1 <- names(CNEA.liste)
  
  checkboxGroupInput("C.define", label = p("3. Select carbon standards"), 
    choices = level.identifier.1,
    selected = level.identifier.1[1],
    inline = F)
  
  } else {}
})

output$Value.C <- renderUI({
  
  if(!is.null(input$CNEA) & !is.null(input$C.define)) {
  
  CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
  
  level.identifier.1 <- names(CNEA.liste)
  
  plot_output_list <- lapply(seq(from = 1, to = length(input$C.define), by = 1), function(i) {
								V.C <- paste("value.C", i, sep="")
								textInput(V.C, label = "", value = paste("Value C for ", input$C.define[i]))
    })
  
  } else {}
})

c.ToTake <- reactive({
  
  if(!is.null(input$CNEA) & !is.null(input$C.define)) {
    
  CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
    
  level.identifier.1 <- names(CNEA.liste)
  
  c.ToTake <- sapply(1:length(input$C.define), function(x) {
    which(input$C.define[x] == level.identifier.1)
  })
  c.ToTake <- sort(c.ToTake)
  
  return(c.ToTake) ## rank of value to take
  
  } else {}
})

value.C <- reactive({
  
  if(!is.null(input$CNEA) & !is.null(input$C.define)) {
    
  CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
    
  level.identifier.1 <- names(CNEA.liste)
  
  temp <- vector()
  
  for(i in 1:length(input$C.define)){

    temp <- c(temp, eval(parse(text = paste("input$value.C", i, sep=""))))

  }
  
  return(temp)
  
  } else {}
})

value.C.toTake <- reactive({
  
  if(!is.null(input$CNEA) & !is.null(input$C.define)) {
    
    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
    
    level.identifier.1 <- names(CNEA.liste)
    
    temp <- value.C()
  
  # temp <- value.C()[c.ToTake()]
  # 
  # names(temp) <- level.identifier.1[c.ToTake()]
  
  return(temp)
  
  } else {}
  
})

nameInput.N <- reactive({
  
  if(!is.null(input$N.define)) {

  nameInput <- vector()

    for(i in 1:length(input$N.define)) {
      nameInput[i] <- paste0(resultMatrix()$Identifier.1[which(input$N.define[i] == resultMatrix()$Identifier.1)], "_inputName.N")
    }
  
  return(nameInput)
  
  }
  
})

output$chooseValue.N.stand <- renderUI({
  
  if(!is.null(input$CNEA) & !is.null(input$N.define)) {

  lapply(1:length(input$N.define), function(x){

    div(
      column(6, p(paste("Select the values that you want to keep for", resultMatrix()$Identifier.1[which(input$N.define[x] == resultMatrix()$Identifier.1)]))),
      column(6,
             checkboxGroupInput(nameInput.N()[x], label = p(""),
                                choices = resultMatrix()$d15N[which(input$N.define[x] == resultMatrix()$Identifier.1)],
                                selected = resultMatrix()$d15N[which(input$N.define[x] == resultMatrix()$Identifier.1)],
                                inline = T),
             br()
    )

    )
    })
  }
})

output$checkBox.N <- renderUI({
  
  if(!is.null(input$CNEA)) {
  
    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
    
    level.identifier.1 <- names(CNEA.liste)
    
    checkboxGroupInput("N.define", label = p("4. Select nitrogen standards"), 
    choices = level.identifier.1,
    selected = level.identifier.1[1],
    inline = F)
    
  } else {}
})

output$Value.N <- renderUI({
  
  if(!is.null(input$CNEA) & !is.null(input$N.define)) {
    
    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
    
    level.identifier.1 <- names(CNEA.liste)
    
  plot_output_list <- lapply(seq(from = 1, to = length(input$N.define), by = 1), function(i) {
								V.N <- paste("value.N", i, sep="")
								textInput(V.N, label = "", value = paste("Value N for ", input$N.define[i]))
    })
  
  } else {}
})

n.ToTake <- reactive({
    
  if(!is.null(input$CNEA) & !is.null(input$N.define)) {
    
    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
    
    level.identifier.1 <- names(CNEA.liste)
  
  n.ToTake <- sapply(1:length(input$N.define), function(x) {
    which(input$N.define[x] == level.identifier.1)
  })
  n.ToTake <- sort(n.ToTake)
  
  return(n.ToTake) ## rank of value to take
  
  } else {}
})

value.N <- reactive({
  
  if(!is.null(input$CNEA) & !is.null(input$N.define)) {
    
    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
    
    level.identifier.1 <- names(CNEA.liste)
  
  temp <- vector()
  
  for(i in 1:length(input$N.define)){

    temp <- c(temp, eval(parse(text = paste("input$value.N", i, sep=""))))

  }
  
  return(temp)
  
  } else {}
})

value.N.toTake <- reactive({
  
  if(!is.null(input$CNEA) & !is.null(input$N.define)) {  
  
    CNEA.liste <- split(CNEA(), CNEA()$Identifier.1)
    
    level.identifier.1 <- names(CNEA.liste)
    
    temp <- value.N()
  
  # temp <- value.N()[n.ToTake()]
  
  # names(temp) <- level.identifier.1[n.ToTake()]
  
  return(temp)
  
  } else {}
  
})
```
`r div(column(6, uiOutput("checkBox.N")), column(6, uiOutput("Value.N")))` 
`r div(column(12, uiOutput("chooseValue.N.stand")))`
<br><br>
`r div(column(6, uiOutput("checkBox.C")), column(6, uiOutput("Value.C")))`
`r div(column(12, uiOutput("chooseValue.C.stand")))`
<br><br>

```{r}
#############################################################################################################################
### Table1 is the first table of the isotope data sheet that allow to have the average of the NItrogen and Carbon standards
#############################################################################################################################

table1 <- reactive({
  
  if(!is.null(input$CNEA)) {
  
  nitrogen.table1 <- list()

for(i in 1:length(input$N.define)) {
  
  nitrogen.table1[[i]] <- eval(parse(text = paste0("input$\'", nameInput.N()[i], "\'")))
  
}

carbon.table1 <- list()

for(i in 1:length(input$C.define)) {
  
  carbon.table1[[i]] <- eval(parse(text = paste0("input$\'", nameInput.C()[i], "\'")))
  
}

nrow.table1 <- max(max.list(nitrogen.table1), max.list(carbon.table1)) + 5
ncol.table1 <- length(input$C.define) + length(input$N.define)+1

table1 <- as.data.frame(matrix(ncol = ncol.table1, nrow = nrow.table1)) ## Blank corrected delta values for isotope standards

table1[1,] <- c("Blank corrected delta values for isotope standards", rep("Nitrogen", length(input$N.define)), rep("Carbon", length(input$C.define)))
table1[2,] <- c(" ", input$N.define, input$C.define)

for(i in 1:length(input$N.define)) {
  
  table1[3:(2+length(nitrogen.table1[[i]])),i+1] <- as.character(nitrogen.table1[[i]])
  
}

for(i in 1:length(input$C.define)) {
  
  table1[3:(2+length(carbon.table1[[i]])),i+length(input$N.define)+1] <- as.character(carbon.table1[[i]])
  
}

table1[3:(nrow(table1)-3),1] <- " "

table1[(nrow(table1)-2) : nrow(table1), 1] <- c("Average", "Stdev", "True.Value")

for(i in 2:(length(input$C.define) + length(input$N.define) + 1)) {
  
  analysis <- as.numeric(as.character(table1[,i]))
  
  table1[(nrow.table1-2),i] <- round(mean(analysis, na.rm = T), digits = 2)
  table1[(nrow.table1-1),i] <- round(sd(analysis, na.rm = T), digits = 2)
}

table1[nrow.table1,(2:ncol.table1)] <- c(as.numeric(as.character(value.N.toTake())), as.numeric(as.character(value.C.toTake())))

colnames(table1) <- c("Names", paste("Nitrogen", input$N.define, sep ="."), paste("Carbon", input$C.define, sep ="."))

return(table1)

  if(input$nameSession == "Name of the session") {
    toAdd <- ""
  } else {
    toAdd <- input$nameSession
  }

  } else {}
  
})

output$table1.toDisplay <- renderDT({
 table1()
})
```
`r DTOutput("table1.toDisplay")`

```{r}
#############################################################################################################################
### creation of the table2: table2.standard (i.e. called Blank correction of delta value in standards) and table2.sample
#############################################################################################################################

table2 <- reactive({
  
  if(!is.null(resultMatrix())) {
    resultMatrix <- resultMatrix()[order(as.numeric(as.character(resultMatrix()$FirstLine))),]

  line.sample  <- lapply(1:length(input$sample), function(x) {
    which(resultMatrix$Identifier.1 == input$sample [x])
    }) # the line of the resultMatrix that correspond to the sample

  line.sample <- unlist(line.sample)

  table2.sample.Temp <- resultMatrix[line.sample,]

  table2.sample.Temp <- table2.sample.Temp[order(as.numeric(as.character(table2.sample.Temp$FirstLine))),]

  line.standard <- complementVector(1:nrow(resultMatrix), line.sample)

  table2.standard.Temp <- resultMatrix[line.standard,]

  table2.standard.Temp <- table2.standard.Temp[order(as.numeric(as.character(table2.standard.Temp$FirstLine))),]

  # table2.standard final (i.e. with corrected value)

  table2.standard <- as.data.frame(matrix(ncol = 16, nrow = nrow(table2.standard.Temp)))

  colnames(table2.standard) <- c("Box.No", "Box.position", "sample.name", "sample.weight","Area.N", "d14N.d15N.ratio", "d14N.d15N.BlankCorrected", "Normalized.d14N.d15N", "At.N", "equipement.dilution", "Area.C", "d12C.d13C.ratio", "Area.C.Corrected", "d12C.d13C.BlankCorrected", "Normalized.d12C.d13C", "At.C")

  table2.standard$Box.No <- " "
  table2.standard$Box.position <- " "
  
  table2.standard[,3] <- as.character(table2.standard.Temp$Identifier.1)
  table2.standard[,5] <- as.numeric(as.character(table2.standard.Temp$Area.N))
  table2.standard[,6] <- as.numeric(as.character(table2.standard.Temp$d15N))
  table2.standard[,10] <- as.numeric(as.character(table2.standard.Temp$Dilution))
  table2.standard[,11] <- as.numeric(as.character(table2.standard.Temp$Area.C))
  table2.standard[,12] <- as.numeric(as.character(table2.standard.Temp$d13C))

  blank.correction <- function(Area.blank, Sign.blank, Area.sample, Sign.sample) {
  value <- (Area.sample*Sign.sample - Area.blank*Sign.blank)/(Area.sample - Area.blank)
  return(value)
  }

  blankValue.N <- c(as.numeric(as.character(input$Area.N.background)), as.numeric(as.character(input$signature.N.background)))

  if(is.na(blankValue.N)) {
    blankValue.N <- c(0, 0)
  }

  blankValue.C <- c(as.numeric(as.character(input$Area.C.background)), as.numeric(as.character(input$signature.C.background)))

    if(is.na(blankValue.C)) {
    blankValue.C <- c(0, 0)
    }

  toConvert <- c(5,6, 10, 11, 12)

  for(i in 1:length(toConvert)) {
    table2.standard[,toConvert[i]] <-as.numeric(as.character(table2.standard[,toConvert[i]]))
  }

 ## Blank correction d15N

  blankCorrected.d15N <- sapply(1:nrow(table2.standard), function(x) {
    blank.correction(blankValue.N[1], blankValue.N[2], table2.standard$Area.N[x],table2.standard$d14N.d15N.ratio[x])
  })

  table2.standard$d14N.d15N.BlankCorrected <- blankCorrected.d15N

  ## Area Correction d13C

  Area.Corrected.d13C <- sapply(1:nrow(table2.standard), function(x) {
    Area.correction(table2.standard$Area.C[x], table2.standard$equipement.dilution[x])
  })

  table2.standard$Area.C.Corrected <- Area.Corrected.d13C

  ## blank correction d13C

  blankCorrected.d13C <- sapply(1:nrow(table2.standard), function(x) {
    blank.correction(blankValue.C[1], blankValue.C[2], table2.standard$Area.C.Corrected[x],table2.standard$d12C.d13C.ratio[x])
  })

  table2.standard$d12C.d13C.BlankCorrected <- blankCorrected.d13C
  
  # table2.sample final (i.e. with corrected value)

  table2.sample <- as.data.frame(matrix(ncol = 16, nrow = nrow(table2.sample.Temp)))

  colnames(table2.sample) <- c("Box.No", "Box.position", "sample.name", "sample.weight","Area.N", "d14N.d15N.ratio", "d14N.d15N.BlankCorrected", "Normalized.d14N.d15N", "At.N", "equipement.dilution", "Area.C", "d12C.d13C.ratio", "Area.C.Corrected", "d12C.d13C.BlankCorrected", "Normalized.d12C.d13C", "At.C")

  table2.sample[,1] <- as.character(table2.sample.Temp$Identifier.1)
  table2.sample[,2] <- as.character(table2.sample.Temp$Identifier.2)
  table2.sample[,3] <- as.character(weightData()$Name)
  table2.sample[,4] <- as.numeric(as.character(weightData()$Measured.Weigth..mg.))
  table2.sample[,5] <- as.numeric(as.character(table2.sample.Temp$Area.N))
  table2.sample[,6] <- as.numeric(as.character(table2.sample.Temp$d15N))
  table2.sample[,10] <- as.numeric(as.character(table2.sample.Temp$Dilution))
  table2.sample[,11] <- as.numeric(as.character(table2.sample.Temp$Area.C))
  table2.sample[,12] <- as.numeric(as.character(table2.sample.Temp$d13C))

  toConvert <- c(5,6, 10, 11, 12)

  for(i in 1:length(toConvert)) {
    table2.sample[,toConvert[i]] <-as.numeric(as.character(table2.sample[,toConvert[i]]))
  }

# blank correction d15N

  blankCorrected.d15N <- sapply(1:nrow(table2.sample), function(x) {
    blank.correction(blankValue.N[1], blankValue.N[2], table2.sample$Area.N[x],table2.sample$d14N.d15N.ratio[x])
  })

  table2.sample$d14N.d15N.BlankCorrected <- blankCorrected.d15N

  ## Area Correction d13C

  Area.Corrected.d13C <- sapply(1:nrow(table2.sample), function(x) {
    Area.correction(table2.sample$Area.C[x], table2.sample$equipement.dilution[x])
  })

  table2.sample$Area.C.Corrected <- Area.Corrected.d13C

  ## blank correction d13C

  blankCorrected.d13C <- sapply(1:nrow(table2.sample), function(x) {
    blank.correction(blankValue.C[1], blankValue.C[2], table2.sample$Area.C.Corrected[x],table2.sample$d12C.d13C.ratio[x])
  })

  table2.sample$d12C.d13C.BlankCorrected <- blankCorrected.d13C

  Rank.Analysis <- seq(1,nrow(table2.sample))

  table2.sample <- cbind(Rank.Analysis, table2.sample)
  
   return(list(table2.standard, table2.sample))
  } else {NULL}

  
})

table2.standard <- reactive({
  table2()[[1]]
})

table2.sample <- reactive({
  table2()[[2]]
})

dilution <- reactive ({
  gelA.lines <- NULL

  for(i in 1:length(input$gelA)) {

  gelA.lines <- c(gelA.lines, which(table2.sample()$sample.name == input$gelA[i]))

}

gelA.table <- table2.sample()[gelA.lines,]

table.WithoutGelA <- table2.sample()[complementVector(1:nrow(table2.sample()), gelA.lines),]

## table of the dilution

dilution.Sample <- vector()

dilution.factor <- length(levels(as.factor(table.WithoutGelA$equipement.dilution)))

for(i in i:dilution.factor) {
  dilution.Sample[i] <- length(which(table.WithoutGelA$equipement.dilution == as.numeric(as.character(levels(as.factor(table.WithoutGelA$equipement.dilution))[i]))))
}

names(dilution.Sample) <- levels(as.factor(table.WithoutGelA$equipement.dilution))

dilution.Sample <- t(as.matrix(dilution.Sample))

rownames(dilution.Sample) <- "Number of sample analyzed with this dilution"

return(list(dilution.Sample, gelA.table, table.WithoutGelA))
})

gelA.table <- reactive({
  dilution()[[2]]
})

table.WithoutGelA <- reactive({
  dilution()[[3]]
})

output$dilutionTable <- renderTable({
  
  if(!is.null(resultMatrix())) {
  dilution()[[1]]
    
  }
}, include.rownames=TRUE)

```

------------------------------------------------------------------------------------------------------------------------------

### Karina's procedure of Normalization
<br>
Normalized.signature =  (Stand.1_TRUE - Stand.2_TRUE)/(Stand.1_OBS - Stand.2_OBS) * (signature - Stand.1_OBS) + Stand.1_TRUE
<br><br>
At (d15N) = 100/(271.872114/(1+(Normalized.signature/1000))+1)<br>
At (d13N) = 100/(89.443838/(1+(Normalized.signature/1000))+1)

```{r}
table2.sample.Karina <- reactive({

table2.sample.Karina <- table2.sample()

norm.Karina.d15N <- sapply(1:nrow(table2.sample.Karina), function(x) {
  Karina.Normalisation(signature = table2.sample.Karina$d14N.d15N.BlankCorrected[x], true.Values = as.numeric(as.character(table1()[nrow(table1()),2:3])), real.Values =
as.numeric(as.character(table1()[(nrow(table1())-2),2:(length(input$N.define) +1)])))
})

table2.sample.Karina$Normalized.d14N.d15N <- norm.Karina.d15N

At.d15N <- 100/(271.872114/(1+(table2.sample.Karina$Normalized.d14N.d15N/1000))+1)

table2.sample.Karina$At.N <- At.d15N

norm.Karina.d13C <-  sapply(1:nrow(table2.sample.Karina), function(x) {
  Karina.Normalisation(signature = table2.sample.Karina$d12C.d13C.BlankCorrected[x], true.Values = as.numeric(as.character(table1()[nrow(table1()),4:5])), real.Values = as.numeric(as.character(table1()[(nrow(table1())-2),(length(input$N.define) +2):(length(input$N.define) +3)])))
})

table2.sample.Karina$Normalized.d12C.d13C <- norm.Karina.d13C

At.d13C <- 100/(89.443838/(1+(table2.sample.Karina$Normalized.d12C.d13C/1000))+1)

table2.sample.Karina$At.C <- At.d13C

return(table2.sample.Karina)
})

output$dataSampleKarina <- renderDT({
   if(length(input$C.define) > 1 & length(input$N.define) > 1 ) {
     
  if(input$nameSession == "Name of the session") {
    toAdd <- ""
  } else {
    toAdd <- input$nameSession
  }
     
     table0 <- matrix("", 20, 2)
     
table0[,1] <- c("Total C and D Isotope Analysis", 
                "", 
                "1. Session settings",
                "Date", 
                "Samples", 
                "Responsible", 
                "Lab. Temp", 
                "System", 
                "Column", 
                "Temp, Owen", 
                "Carrier gas", 
                "Carrier flow", 
                "Reference gas1",
                "Reference flow", 
                "Reference gas2",
                "Reference flow", 
                "Method", 
                "", "",
                "2. Blank corrected delta values for isotope standards"
)
table0[,2] <- c("", 
                "", 
                "", 
                input$dateProcessig, 
                input$SampleName, 
                input$Responsible, 
                input$Temperature, 
                input$system, 
                input$Column, 
                input$temp.Owen, 
                input$carrier.Gas, 
                input$carrier.flow, 
                input$Reference.gas1,
                input$Reference.flow1, 
                input$Reference.gas2,
                input$Reference.flow2, 
                input$Method, 
                "", "", 
                ""
)
table1_new <- table1()

lapply(2:ncol(table1_new), function(x) {
  table1_new[3:nrow(table1_new),x] <- as.numeric(as.character(table1_new[3:nrow(table1_new), x]))
})
table1_new[1:2,1] <- c("Isotope", "Standard")


table2.standard_new <- table2.standard()
lapply(5:ncol(table2.standard_new), function(x) {
  table2.standard_new[1:nrow(table2.standard_new), x] <- as.numeric(as.character(table2.standard_new[1:nrow(table2.standard_new), x]))
})

table2.sample.Karina_new <- table2.sample.Karina()
lapply(5:ncol(table2.sample.Karina_new), function(x) {
  table2.sample.Karina_new[1:nrow(table2.sample.Karina_new), x] <- as.numeric(as.character(table2.sample.Karina_new[1:nrow(table2.sample.Karina_new), x]))
})

table.Interm1 <- matrix("3. Blank correction of delta value in standards", ncol = 1, nrow = 1)
table.Interm2 <- matrix("4. Results from samples", ncol = 1, nrow = 1)

normStyle <- createStyle(valign = "center", halign = "center", numFmt = "0.00")
GeneraltitleStyle <- createStyle(valign = "center", halign = "center", fontSize = 14, textDecoration = "bold")
titleStyle <- createStyle(valign = "center", halign = "left", fontSize = 14, textDecoration = "bold")
tableStyle <- createStyle(borderStyle = "thin", border = "TopBottomLeftRight")

colorBlue <- createStyle(fgFill = "#99ccff")
colorGreen <- createStyle(fgFill = "#00ff00")

wb <- createWorkbook("Example.xlsx")

addWorksheet(wb, "CNEA_data")
writeData(wb, sheet = 1, CNEA(), colNames = T)

addWorksheet(wb, "isotope_data")

writeData(wb, sheet = 2, table0, colNames = FALSE)
writeData(wb, sheet = 2, table1_new, startRow = nrow(table0) + 1, colNames = F)
writeData(wb, sheet = 2, table.Interm1, startRow = nrow(table0) + nrow(table1_new) + 3, colNames = F)
writeData(wb, sheet = 2, table2.standard_new, startRow = nrow(table0) + nrow(table1_new) + 4, colNames = T)
writeData(wb, sheet = 2, table.Interm2, startRow = nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 7, colNames = F)
writeData(wb, sheet = 2, table2.sample.Karina_new, startRow = nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 8, colNames = T)


nbRow_FinalTable <- nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + nrow(table2.sample.Karina_new) + 8

lapply(1:17, function(x) {
  addStyle(wb, sheet = 2, normStyle, cols = x, rows = 1:nbRow_FinalTable)
})

addStyle(wb, sheet = 2, GeneraltitleStyle, rows = 1, cols = 1, stack = T)
addStyle(wb, sheet = 2, titleStyle, rows = 20, cols = 1, stack = T)
addStyle(wb, sheet = 2, titleStyle, rows = nrow(table0) + nrow(table1_new) + 3, cols = 1, stack = T)
addStyle(wb, sheet = 2, titleStyle, rows = nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 7, cols = 1, stack = T)

table1_end <- nrow(table0) + nrow(table1_new)

lapply(1:5, function(x) {
  addStyle(wb, sheet = 2, tableStyle, cols = x, rows = 21:table1_end, stack = T)
})

table2_stand_begin <- nrow(table0) + nrow(table1_new) + 4
table2_stand_end <- nrow(table0) + nrow(table1_new) + 4 + nrow(table2.standard_new)

lapply(1:16, function(x) {
  addStyle(wb, sheet = 2, tableStyle, rows = table2_stand_begin:table2_stand_end, cols = x, stack = T)
})

addStyle(wb, sheet = 2, colorBlue, cols = 8, rows = table2_stand_begin:table2_stand_end, stack = T)
addStyle(wb, sheet = 2, colorBlue, cols = 15, rows = table2_stand_begin:table2_stand_end, stack = T)
addStyle(wb, sheet = 2, colorGreen, cols = 9, rows = table2_stand_begin:table2_stand_end, stack = T)
addStyle(wb, sheet = 2, colorGreen, cols = 16, rows = table2_stand_begin:table2_stand_end, stack = T)

table2_sample_begin <- nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 8
table2_sample_end <-  nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 8 + nrow(table2.sample.Karina_new)

lapply(1:17, function(x) {
  addStyle(wb, sheet = 2, tableStyle, rows = table2_sample_begin:table2_sample_end, cols = x, stack = T)
})

addStyle(wb, sheet = 2, colorBlue, cols = 9, rows = table2_sample_begin:table2_sample_end, stack = T)
addStyle(wb, sheet = 2, colorBlue, cols = 16, rows = table2_sample_begin:table2_sample_end, stack = T)
addStyle(wb, sheet = 2, colorGreen, cols = 10, rows = table2_sample_begin:table2_sample_end, stack = T)
addStyle(wb, sheet = 2, colorGreen, cols = 17, rows = table2_sample_begin:table2_sample_end, stack = T)

mergeCells(wb, sheet = 2, cols = 1:18, rows = 1)
mergeCells(wb, sheet = 2, cols = 1:8, rows = 20)
mergeCells(wb, sheet = 2, cols = 1:8, rows = nrow(table0) + nrow(table1_new) + 3)
mergeCells(wb, sheet = 2, cols = 1:8, rows = nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 7)

mergeCells(wb, sheet = 2, cols = 2:3, rows = 21)
mergeCells(wb, sheet = 2, cols = 4:5, rows = 21)


saveWorkbook(wb, file = paste0("table2.sample.Karina_",toAdd, ".xlsx" ), overwrite = TRUE)
  table2.sample.Karina()
} else {}
})

```
#### Final Table
`r DTOutput("dataSampleKarina")`

------------------------------------------------------------------------------------------

### Peter's procedure of Normalization
<br>
Here, the user has to select the relevant dilution to keep in the linear regression
`r tableOutput('dilutionTable')`
Define the dilution factor to consider for the normalization: 
`r uiOutput('choiceDilution')`


```{r}

output$choiceDilution <- renderUI({
  
  if(!is.null(resultMatrix())) {
    
      dilution.suggested <- levels(as.factor(gelA.table()$equipement.dilution))
  
  toPick.dilution <- dilution.suggested[which(dilution.suggested != "0" & dilution.suggested != " " & dilution.suggested != "" & !is.na(dilution.suggested))]
  
  checkboxGroupInput("dilutionPicked", label = "",
                   choices = toPick.dilution,
                   selected = toPick.dilution[1],
                   inline = TRUE)
    
  }
})

gelA.table.dilution <- reactive({
  
  if(!is.null(resultMatrix())) {
  
  toConsider <-lapply(1:length(input$dilutionPicked), function(x) {
    which(gelA.table()$equipement.dilution == input$dilutionPicked[x])
  })
  
  toConsider <- unlist(toConsider)
  
  gelA.table.dilution <- gelA.table()[toConsider, ]
  
  gelA.table.dilution <- gelA.table.dilution[order(gelA.table.dilution$Rank.Analysis),]
  
  return(gelA.table.dilution)
  
  }
})

output$GelA.tokeep.N <- renderUI({
  
  if(!is.null(gelA.table.dilution())) {
               checkboxGroupInput("GelA.tokeep.N", label = p("Select the gelA to keep for the linear regression"),
                                choices = gelA.table.dilution()$Box.position,
                                selected = gelA.table.dilution()$Box.position, 
                                inline = T )
    
  } else {}
})

gelA.dilution_toKeep.N <- reactive({
  
  if(!is.null(resultMatrix()) & !is.null(input$GelA.tokeep.N)) {
  
  toConsider <-lapply(1:length(input$GelA.tokeep.N), function(x) {
      which(gelA.table.dilution()$Box.position == input$GelA.tokeep.N[x])
  })
  
  toConsider <- unlist(toConsider)
  
  gelA.dilution_toKeep <- gelA.table.dilution()[toConsider, ]
  
  gelA.dilution_toKeep <- gelA.dilution_toKeep[order(gelA.dilution_toKeep$Rank.Analysis),]
  
  return(gelA.dilution_toKeep)
  
  }
})

gelA.dilution_toKeep.C <- reactive({
  
  if(!is.null(resultMatrix()) & !is.null(input$GelA.tokeep.C)) {
  
  toConsider <-lapply(1:length(input$GelA.tokeep.C), function(x) {
      which(gelA.table.dilution()$Box.position == input$GelA.tokeep.C[x])
  })
  
  toConsider <- unlist(toConsider)
  
  gelA.dilution_toKeep <- gelA.table.dilution()[toConsider, ]
  
  gelA.dilution_toKeep <- gelA.dilution_toKeep[order(gelA.dilution_toKeep$Rank.Analysis),]
  
  return(gelA.dilution_toKeep)
  
  }
})

output$GelA.tokeep.C <- renderUI({
  
  if(!is.null(gelA.table.dilution())) {
               checkboxGroupInput("GelA.tokeep.C", label = p("Select the gelA to keep for the linear regression"),
                                choices = gelA.table.dilution()$Box.position,
                                selected = gelA.table.dilution()$Box.position, 
                                inline = T )
    
  } else {}
})

model.15N <- reactive({
  
  if(!is.null(gelA.dilution_toKeep.N())) {
  
  model.d15N <- lm(gelA.dilution_toKeep.N()$d14N.d15N.BlankCorrected ~ gelA.dilution_toKeep.N()$Rank.Analysis)
  Intercept.N <- summary(model.d15N)$coefficients[1]
  Slope.N <- summary(model.d15N)$coefficients[2]
  return(c(Intercept.N, Slope.N))
    
  }
})

model.13C <- reactive({
  
  if(!is.null(gelA.dilution_toKeep.C())) {
    
  model.d13C <- lm(gelA.dilution_toKeep.C()$d12C.d13C.BlankCorrected ~ gelA.dilution_toKeep.C()$Rank.Analysis)
  Intercept.C <- summary(model.d13C)$coefficients[1]
  Slope.C <- summary(model.d13C)$coefficients[2]
  return(c(Intercept.C, Slope.C))
  
  }
})

output$linearRegression.N <- renderPlot({
  
  if(!is.null(gelA.dilution_toKeep.N())) {
  
    plot(gelA.dilution_toKeep.N()$d14N.d15N.BlankCorrected ~ gelA.dilution_toKeep.N()$Rank.Analysis, ylab = "d14N.d15N.BlankCorrected", xlab = "Rank.Analysis")
    text(gelA.dilution_toKeep.N()$Rank.Analysis, gelA.dilution_toKeep.N()$d14N.d15N.BlankCorrected, labels=gelA.dilution_toKeep.N()$Box.position, cex= 0.7, pos=4)
    abline(model.15N()[1], model.15N()[2], col = 'red')
    
  }
  
})

output$linearRegression.C <- renderPlot({
  
  if(!is.null(gelA.dilution_toKeep.C())) {
  
    plot(gelA.dilution_toKeep.C()$d12C.d13C.BlankCorrected ~ gelA.dilution_toKeep.C()$Rank.Analysis, ylab = "d12C.d13C.BlankCorrected", xlab = "Rank.Analysis")
    text(gelA.dilution_toKeep.C()$Rank.Analysis, gelA.dilution_toKeep.C()$d12C.d13C.BlankCorrected, labels=gelA.dilution_toKeep.C()$Box.position, cex= 0.7, pos=4)
    abline(model.13C()[1], model.13C()[2], col = 'red')
    
  }

})

table2.sample.Peter <- reactive({
  
  if(!is.null(model.15N()) & !is.null(model.13C())) {
  
  table2.sample.Peter <- table2.sample()
  
  Norm.d15N <- Peter.Correction.d15N(table2.sample.Peter$d14N.d15N.BlankCorrected, table2.sample.Peter$Rank.Analysis, model.15N()[2], model.15N()[1])
  
  table2.sample.Peter$Normalized.d14N.d15N <- Norm.d15N

  Norm.d13C <- Peter.Correction.d13C(table2.sample.Peter$d12C.d13C.BlankCorrected, table2.sample.Peter$Rank.Analysis, model.13C()[2], model.13C()[1])

  table2.sample.Peter$Normalized.d12C.d13C <- Norm.d13C
  
  return(table2.sample.Peter)
    
  }
})

output$modelN <- renderText({
  
  if(!is.null(model.15N()) & !is.null(model.13C())) {
  
    paste("For N, the parameters of the model: intercept = ", round(model.15N()[1],10), " and slope = ", round(model.15N()[2], 10))
    
  }
})

output$modelC <- renderText({
  
   if(!is.null(model.15N()) & !is.null(model.13C())) {
  
  paste("For C, the parameters of the model: intercept = ", round(model.13C()[1],10), " and slope = ", round(model.13C()[2], 10))
     
   }
})

output$FinalTable <- renderDT({
  
  if(!is.null(table2.sample.Peter())) {
      if(input$nameSession == "Name of the session") {
    toAdd <- ""
  } else {
    toAdd <- input$nameSession
  }
    
    table0 <- matrix("", 20, 2)
     
table0[,1] <- c("Total C and D Isotope Analysis", 
                "", 
                "1. Session settings",
                "Date", 
                "Samples", 
                "Responsible", 
                "Lab. Temp", 
                "System", 
                "Column", 
                "Temp, Owen", 
                "Carrier gas", 
                "Carrier flow", 
                "Reference gas1",
                "Reference flow", 
                "Reference gas2",
                "Reference flow", 
                "Method", 
                "", "",
                "2. Blank corrected delta values for isotope standards"
)
table0[,2] <- c("", 
                "", 
                "", 
                input$dateProcessig, 
                input$SampleName, 
                input$Responsible, 
                input$Temperature, 
                input$system, 
                input$Column, 
                input$temp.Owen, 
                input$carrier.Gas, 
                input$carrier.flow, 
                input$Reference.gas1,
                input$Reference.flow1, 
                input$Reference.gas2,
                input$Reference.flow2, 
                input$Method, 
                "", "", 
                ""
)
table1_new <- table1()

lapply(2:ncol(table1_new), function(x) {
  table1_new[3:nrow(table1_new),x] <- as.numeric(as.character(table1_new[3:nrow(table1_new), x]))
})
table1_new[1:2,1] <- c("Isotope", "Standard")


table2.standard_new <- table2.standard()
lapply(5:ncol(table2.standard_new), function(x) {
  table2.standard_new[1:nrow(table2.standard_new), x] <- as.numeric(as.character(table2.standard_new[1:nrow(table2.standard_new), x]))
})

table2.sample.Peter_new <- table2.sample.Peter()
lapply(5:ncol(table2.sample.Peter_new), function(x) {
  table2.sample.Peter_new[1:nrow(table2.sample.Peter_new), x] <- as.numeric(as.character(table2.sample.Peter_new[1:nrow(table2.sample.Peter_new), x]))
})

table.Interm1 <- matrix("3. Blank correction of delta value in standards", ncol = 1, nrow = 1)
table.Interm2 <- matrix("4. Results from samples", ncol = 1, nrow = 1)

normStyle <- createStyle(valign = "center", halign = "center", numFmt = "0.00")
GeneraltitleStyle <- createStyle(valign = "center", halign = "center", fontSize = 14, textDecoration = "bold")
titleStyle <- createStyle(valign = "center", halign = "left", fontSize = 14, textDecoration = "bold")
tableStyle <- createStyle(borderStyle = "thin", border = "TopBottomLeftRight")

colorBlue <- createStyle(fgFill = "#99ccff")
colorGreen <- createStyle(fgFill = "#00ff00")

wb <- createWorkbook("Example.xlsx")

addWorksheet(wb, "CNEA_data")
writeData(wb, sheet = 1, CNEA(), colNames = T)

addWorksheet(wb, "isotope_data")

writeData(wb, sheet = 2, table0, colNames = FALSE)
writeData(wb, sheet = 2, table1_new, startRow = nrow(table0) + 1, colNames = F)
writeData(wb, sheet = 2, table.Interm1, startRow = nrow(table0) + nrow(table1_new) + 3, colNames = F)
writeData(wb, sheet = 2, table2.standard_new, startRow = nrow(table0) + nrow(table1_new) + 4, colNames = T)
writeData(wb, sheet = 2, table.Interm2, startRow = nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 7, colNames = F)
writeData(wb, sheet = 2, table2.sample.Peter_new, startRow = nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 8, colNames = T)


nbRow_FinalTable <- nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + nrow(table2.sample.Peter_new) + 8

lapply(1:17, function(x) {
  addStyle(wb, sheet = 2, normStyle, cols = x, rows = 1:nbRow_FinalTable)
})

addStyle(wb, sheet = 2, GeneraltitleStyle, rows = 1, cols = 1, stack = T)
addStyle(wb, sheet = 2, titleStyle, rows = 20, cols = 1, stack = T)
addStyle(wb, sheet = 2, titleStyle, rows = nrow(table0) + nrow(table1_new) + 3, cols = 1, stack = T)
addStyle(wb, sheet = 2, titleStyle, rows = nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 7, cols = 1, stack = T)

table1_end <- nrow(table0) + nrow(table1_new)

lapply(1:5, function(x) {
  addStyle(wb, sheet = 2, tableStyle, cols = x, rows = 21:table1_end, stack = T)
})

table2_stand_begin <- nrow(table0) + nrow(table1_new) + 4
table2_stand_end <- nrow(table0) + nrow(table1_new) + 4 + nrow(table2.standard_new)

lapply(1:16, function(x) {
  addStyle(wb, sheet = 2, tableStyle, rows = table2_stand_begin:table2_stand_end, cols = x, stack = T)
})

addStyle(wb, sheet = 2, colorBlue, cols = 8, rows = table2_stand_begin:table2_stand_end, stack = T)
addStyle(wb, sheet = 2, colorBlue, cols = 15, rows = table2_stand_begin:table2_stand_end, stack = T)
addStyle(wb, sheet = 2, colorGreen, cols = 9, rows = table2_stand_begin:table2_stand_end, stack = T)
addStyle(wb, sheet = 2, colorGreen, cols = 16, rows = table2_stand_begin:table2_stand_end, stack = T)

table2_sample_begin <- nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 8
table2_sample_end <-  nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 8 + nrow(table2.sample.Peter_new)

lapply(1:17, function(x) {
  addStyle(wb, sheet = 2, tableStyle, rows = table2_sample_begin:table2_sample_end, cols = x, stack = T)
})

addStyle(wb, sheet = 2, colorBlue, cols = 9, rows = table2_sample_begin:table2_sample_end, stack = T)
addStyle(wb, sheet = 2, colorBlue, cols = 16, rows = table2_sample_begin:table2_sample_end, stack = T)
addStyle(wb, sheet = 2, colorGreen, cols = 10, rows = table2_sample_begin:table2_sample_end, stack = T)
addStyle(wb, sheet = 2, colorGreen, cols = 17, rows = table2_sample_begin:table2_sample_end, stack = T)

mergeCells(wb, sheet = 2, cols = 1:18, rows = 1)
mergeCells(wb, sheet = 2, cols = 1:8, rows = 20)
mergeCells(wb, sheet = 2, cols = 1:8, rows = nrow(table0) + nrow(table1_new) + 3)
mergeCells(wb, sheet = 2, cols = 1:8, rows = nrow(table0) + nrow(table1_new) + nrow(table2.standard_new) + 7)

mergeCells(wb, sheet = 2, cols = 2:3, rows = 21)
mergeCells(wb, sheet = 2, cols = 4:5, rows = 21)


saveWorkbook(wb, file = paste0("table2.sample.Peter_",toAdd, ".xlsx" ), overwrite = TRUE)

  table2.sample.Peter()
  }
})
```


#### 1. Linear regression d15N
<br>
`r uiOutput('GelA.tokeep.N')`
`r textOutput('modelN')`
`r plotOutput('linearRegression.N')`
<br><br>

#### 2. Linear regression d13C
<br>
`r uiOutput('GelA.tokeep.C')`
`r textOutput('modelC')`
`r plotOutput('linearRegression.C')`
<br><br>

#### 3. Final Table
<br>
`r DTOutput("FinalTable")`


------------------------------------------------------------------------------------------------------------------------------

### Data exploration

```{r}
radioButtons("tableChosen",
             label = "Choose the table that you want to explore",
             choices = c("Karina's procedure Table", "Peter's procedure Table"),
             selected = "Peter's procedure Table", inline = T
             )

dataToExplore <- reactive({
  if(input$tableChosen == "Karina's procedure Table") {
    
    if(!is.null(table2.sample.Karina())) {
      output <- table2.sample.Karina()
    } else {NULL}
    
  } else {
    
    if(!is.null(table2.sample.Peter())) {
      
      output <- table2.sample.Peter()
    } else {}
  }
})

output$pivot <- renderRpivotTable({
  if(!is.null(dataToExplore())) {
    rpivotTable(dataToExplore(),width="100%", height="400px")
  } else {}
})

```
`r rpivotTableOutput('pivot')`

<br><br><br><br>

